InteroceptionScale - Data Analysis

### 2024-12-11 study1/analysis/2_analysis.qmd
final

    rez <- rbind(
      MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(items), cor(bymodality),
                                         ncomp1=10, ncomp2=10, plot=FALSE)) |>
      as.data.frame() |>
      mutate(
        Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
        Sample = c("Random", "Random", "Full", "Full"),
        Iteration = i) |>
      mutate(d_PSI = diff(PSI), d_RV = diff(RV), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |>
      rbind(rez)
  }
  rez
}

@@

>>>>

    rez <- rbind(
      MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(items), cor(bymodality),
                                         ncomp1=10, ncomp2=10, plot=FALSE)) |>
      as.data.frame() |>
      mutate(
        Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
        Sample = c("Random", "Random", "Full", "Full"),
        Iteration = i) |>
      mutate(d_PSI = diff(PSI), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |>
      rbind(rez)
  }
  rez
}

@@

### Item Table
